---
output:
  html_document: default
  pdf_document: default
---
### Expression of cell type markers and genes associated with regional brain volume in fetal neocortex

---
  title: "Expression of cell type markers and genes associated with regional brain volume in fetal neocortex"
output:
  html_document: default
github_document: default
---
  
```{r include = FALSE}
### Load data and packages

knitr::opts_chunk$set(fig.width=12, fig.height=8) 

```


```{r, include = FALSE, message = FALSE, warning = FALSE, cache = FALSE}
library(Seurat)
require(gplots)
require(ComplexHeatmap)
require(ggplot2)
require(readxl)
library("dplyr")
require(ComplexHeatmap)
```

We will use the Polioudakis 2019 data to check UMI counts in each cell type for our 4 chosen marker genes HOPX (oRG), EOMES (IP), STMN2 (Neurons), PDGFRA (OPCs):

```{r, include = TRUE, message = FALSE, warning = FALSE, cache = FALSE}

markerGenes = c('HOPX', 'EOMES', 'STMN2', 'PDGFRA')
setwd('/home/jovyan/FetalBrainMarkers/')
load('../data/fetalBrain/Polioudakis/raw_counts_mat.rdata')
metadata = read.delim('../data/fetalBrain/Polioudakis/cell_metadata.csv', sep = ',')
raw_counts_mat = raw_counts_mat[,metadata$Cell]

```

```{r, include = TRUE, message = FALSE, warning = FALSE, cache = FALSE}

df = data.frame(cluster = metadata$Cluster, subcluster = metadata$Subcluster, HOPX = raw_counts_mat['HOPX', ], EOMES = raw_counts_mat['EOMES', ], STMN2 = raw_counts_mat['STMN2', ], PDGFRA = raw_counts_mat['PDGFRA', ])
for (i in 1:length(markerGenes)){
  print(ggplot(df, aes(x=cluster, y=get(markerGenes[i]))) + geom_jitter(size = 0.01) + 
  stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), geom="pointrange", color="red") + 
  ylab(paste(markerGenes[i], 'UMI Count', sep = ' ')) +
  xlab(NULL) + 
  ggtitle(paste(markerGenes[i], 'Expression across Celltypes', sep = ' ')) + 
  theme(axis.text=element_text(size=12)))
}

```

Let's also look how genes associated with regional brain size volume are expressed across our cell types:

```{r, include = TRUE, message = FALSE, warning = FALSE, cache = FALSE}

gwasSummary = read_xlsx('Supp_Table12.xlsx')
gwasGenes = unique(unname(unlist(gwasSummary[,3])))
gwasGenes = gwasGenes[2:length(gwasGenes)]
raw_counts_subset = as.matrix(raw_counts_mat[rownames(raw_counts_mat) %in% gwasGenes,])
meanExpr = do.call("cbind", tapply(metadata$Cell, metadata$Cluster, function(x) rowMeans(raw_counts_subset[,x])))
pdf('BrainSizeGwas.pdf', width = 25, height = 10)
Heatmap(t(meanExpr))
dev.off()
```


